\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-17 doc/paper.Rmd
defining relative optimal locations and expectations
structure

After removing sub-class structure, 
the Chumbley scores is calculated in two steps: an optimization step and a validation step.
In the optimization step, the two markings are aligned horizontally such that within a pre-defined window of length $w_o$ the correlation between $x(t_1)$ and $y(t_2)$ is maximized:
\[
\left(t_1^o, t_2^o\right) = \mathop{\arg \max}\limits_{1 \le t_1 \le T_1, 1 \le t_2 \le T_2} \text{cor} \left(x (t_1, t_1 + w_o), y(t_2, t_2 + w_o) \right)
\]
This results in an optimal vertical (in-phase) shift of $t_1^o - t_2^o$ for aligning the two markings.

@@

@@

# Results

@@

profc20 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:30-c:20.rds")
profc20$coarseness <- 0.2
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:30-c:25.rds")
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:50-c:25.rds")
profc30 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:30.rds")
profc30$coarseness <- .30
profc <- bind_rows(profc20, profc25, profc30)
profc <- profc %>% mutate(
  locations = chumbley %>% purrr::map_int(.f = function(x) {
    res <- NULL
    try(res <- x$locations[1], silent = TRUE)
    res
  })
)
profsumm <- read.csv("../data/profiles-summary.csv")
profsumm <- profsumm %>% select(-run_id)
profc <- profc %>% left_join(profsumm, by=c("land2_id"="land_id", "profile2_id"="profile_id"))

p2 <- profc %>% 
  ggplot(aes(x = locations/(length-wo))) +
  geom_histogram(binwidth = 0.025) +
  facet_grid(.~coarseness, labeller="label_both") + 
  theme_bw() +
  xlab(expression("Relative optimal location "~t^o)) +
  ylab("Number of profiles")

>>>>

After removing sub-class structure, 
the Chumbley scores is calculated in two steps: an optimization step and a validation step.
In the optimization step, the two markings are aligned horizontally such that within a pre-defined window of length $w_o$ the correlation between $x(t_1)$ and $y(t_2)$ is maximized:
\[
\left(t_1^o, t_2^o\right) = \mathop{\arg \max}\limits_{1 \le t_1 \le T_1, 1 \le t_2 \le T_2} \text{cor} \left(x (t_1, t_1 + w_o), y(t_2, t_2 + w_o) \right)
\]
This results in an optimal vertical (in-phase) shift of $t_1^o - t_2^o$ for aligning the two markings. \hh{We will denote the relative optimal locations as $t_1^*$ and $t_2^*$, where $t_i^* = t_i^o/(T_i-w_o)$ for $i=1,2$, such that $t_1^*, t_2^* \in [0,1]$. Once (sub-)class characteristics are removed, the relative optimal locations should be distributed according to a uniform distribution in $[0,1]$. }

@@

\hh{XXX summarise in formula}

@@

## Failed Tests

\hh{number of failed tests for default parameter settings -- XXX what are the defaults? wo:10 percent, coarseness 0.25, wv XXX?}

\hh{diagnose problem: use of optimal location in getting the pairs for different-shift correlations}
\hh{figure: number of diff shift pairs and location}

# A modified test

\hh{fix the algorithm - all of the other properties in Hadler and morris still hold.}

\hh{number of failed tests down. }

# Comparison of Results

@@

profc20 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_20.rds")
profc20$coarseness <- 0.2
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_25.rds")
profc30 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30.rds")
profc30$coarseness <- .30
profc <- bind_rows(profc20, profc25, profc30)
profc <- profc %>% mutate(
  locations = chumbley %>% purrr::map_int(.f = function(x) {
    res <- NULL
    try(res <- x$locations[1], silent = TRUE)
    res
  })
)
profsumm <- read.csv("../data/profiles-summary.csv")
profsumm <- profsumm %>% select(-run_id)
profc <- profc %>% left_join(profsumm, by=c("land2_id"="land_id", "profile2_id"="profile_id"))

p2 <- profc %>% 
  ggplot(aes(x = locations/(length-wo))) +
  geom_histogram(binwidth = 0.025) +
  facet_grid(.~coarseness, labeller="label_both") + 
  theme_bw() +
  xlab(expression("Relative optimal location "~t^*)) +
  ylab("Number of profiles")

### 2018-04-17 doc/paper.tex
structure

After removing sub-class structure, the Chumbley scores is calculated in
two steps: an optimization step and a validation step. In the
optimization step, the two markings are aligned horizontally such that
within a pre-defined window of length \(w_o\) the correlation between
\(x(t_1)\) and \(y(t_2)\) is maximized: \[
\left(t_1^o, t_2^o\right) = \mathop{\arg \max}\limits_{1 \le t_1 \le T_1, 1 \le t_2 \le T_2} \text{cor} \left(x (t_1, t_1 + w_o), y(t_2, t_2 + w_o) \right)
\] This results in an optimal vertical (in-phase) shift of
\(t_1^o - t_2^o\) for aligning the two markings.
\hh{We will denote the relative optimal locations as $t_1^*$ and $t_2^*$, where $t_i^* = t_i^o/T_i$ for $i=1,2$, such that $t_1^*, t_2^* \in [0,1]$. Once (sub-)class characteristics are removed, the relative optimal locations should be distributed according to a uniform distribution in $[0,1]$. }

>>>>

After removing sub-class structure, the Chumbley scores is calculated in
two steps: an optimization step and a validation step. In the
optimization step, the two markings are aligned horizontally such that
within a pre-defined window of length \(w_o\) the correlation between
\(x(t_1)\) and \(y(t_2)\) is maximized: \[
\left(t_1^o, t_2^o\right) = \mathop{\arg \max}\limits_{1 \le t_1 \le T_1, 1 \le t_2 \le T_2} \text{cor} \left(x (t_1, t_1 + w_o), y(t_2, t_2 + w_o) \right)
\] This results in an optimal vertical (in-phase) shift of
\(t_1^o - t_2^o\) for aligning the two markings.
\hh{We will denote the relative optimal locations as $t_1^*$ and $t_2^*$, where $t_i^* = t_i^o/(T_i-w_o)$ for $i=1,2$, such that $t_1^*, t_2^* \in [0,1]$. Once (sub-)class characteristics are removed, the relative optimal locations should be distributed according to a uniform distribution in $[0,1]$. }
